\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-11 paper/ms.tex
Install

\section{Basic usage of DNest4}
The

@@

    return log_L;
}
\end{CodeInput}
\end{CodeChunk}

>>>>

\section{Basic usage of DNest4}
\pkg{DNest4} can be obtained from the \pkg{git} repository at
{\tt https://github.com/eggplantbren/DNest4/} and is licensed under the
MIT license. To obtain \pkg{DNest4} and compile and install the software,
the following steps are sufficient:

\begin{CodeChunk}
\begin{CodeInput}
git clone https://github.com/eggplantbren/DNest4
cd DNest4/code
make
cd ../python
python setup.py install
\end{CodeInput}
\end{CodeChunk}

@@

    return log_L;
}
\end{CodeInput}
\end{CodeChunk}
The dataset is assumed to be accessible inside this function. In the
regression example, this is achieved by having a Data class to represent
datasets. The dataset using the {\em singleton pattern}.
